EvoSuite at the SBST 2015 Tool Competition

### 2015-02-21 papers/sbst15/paper_sbst15.tex
Editing paper

\begin{abstract}
  \EVOSUITE is a mature research prototype that automatically generates unit tests for Java code. 
  This paper summarizes the results and experiences in participating at the third unit testing competition held at SBST 2015,
  where \EVOSUITE ranked second with a $190.6$ score.
\end{abstract}

@@

\EVOSUITE has been evaluated on millions of lines of Java code~\cite{fraser2014large}, both open-source
code and close-source code provided by one of our industrial partners. 
In the previous two editions
of the unit testing tool
competition, \EVOSUITE arrived first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}.

@@

As the generated unit tests are meant for human consumption~\cite{fraser2013does}, \EVOSUITE
applies various post-processing steps to improve readability (e.g.,
minimising) and adds test assertions that capture the current
behavior of the tested classes. To select the most effective
assertions, \EVOSUITE uses mutation
analysis~\cite{10.1109/TSE.2011.93}. 
\EVOSUITE can also be used to automatically find faults in the CUTs~\cite{emse13_oracle}, e.g undeclared
thrown exceptions and broken code contracts.
 For more details on the tool and
its abilities we refer to~\cite{FrA11c}, and for more implementation
details we refer to~\cite{FrA13a}.

@@

The results of \EVOSUITE on the benchmark classes are listed in
Table~\ref{table:results}. On average, \EVOSUITE achieved TODO line
coverage,TODO branch coverage\footnote{Using Cobertura's definition
  of branch coverage, which only counts conditional statements, not
  edges in the CFG.}, and TODO mutation score. On average, \EVOSUITE
produced TODO tests per class, and it took an average of TODO per class to
do so (with \EVOSUITE configured to 3 minutes per class).

\subsection{Classes with No Coverage}

Out of 63 CUTs, \EVOSUITE did not manage to obtain any coverage for 18 classes, i.e. 28\% 
of the total.
For 14 of them (the 7 in the twitter4j and the 7 in the hibernate projects), this is due
to a mismatch in libraries on the classpath. 
In particular, \EVOSUITE does bytecode instrumentation using the ASM library.
However, the projects of the CUTs had their own (older) version of ASM.
This leads to errors like: ``java.lang.IncompatibleClassChangeError: 
class org.objectweb.asm.tree.ClassNode has interface org.objectweb.asm.ClassVisitor as super class''.
Note: \EVOSUITE can handle its own dependencies as CUTs, i.e. by using customized classloaders, 
but only during the search phase.
In the generated JUnit files, those have dependencies to ASM, as we do bytecode instrumentation
even there (e.g., to support environment testing based on mock objects~\cite{arcuri2014automated}).
So, \EVOSUITE does generate tests for those 14 classes, but then all those tests fails due to
that thrown exception.
An easy solution would be to ship \EVOSUITE with its own ASM version using a 
different package name (e.g., by using the JarJar tool\footnote{https://code.google.com/p/jarjar/}).

For the other 4 classes, \EVOSUITE failed to generate any test. These are
\<CharMatcher>, \<CycleHandler>, \<WikipediaInfo> and \<Response>.
There are also a further 4 cases of low coverage (e.g., less than 30\%).
For example, if look at line coverage, then 
we have \<Page> with 1.49\%, \<AbstractInstance> with 13.28\%, \<CategoryDescendantsIterator> with 8.24\%
and \<PageQueryIterable> with 18.57\%.
To improve \EVOSUITE, it will be important to understand why that was the case.

@@

With an overall score of $190.6$, \EVOSUITE achieved the second highest score of all tools in
the competition. The score calculated for best testing is $203.7$:  a very close
call. 
In particular, due to a configuration issue in the classpath of the target projects,
\EVOSUITE could had been run only on 7 out of 9 of the projects used as benchmark.
That is an easily fixed issue that would lead to even higher scores.

>>>>

\begin{abstract}
  \EVOSUITE is a mature research prototype that automatically
  generates unit tests for Java code.  This paper summarizes the
  results and experiences in participating at the third unit testing
  competition held at SBST 2015. An unfortunate issue of conflicting
  dependency versions in two out of the nine projects used in the
  benchmark reduced \EVOSUITE's overall score to $190.6$, and thus the
  second rank.
\end{abstract}

@@

\EVOSUITE has been evaluated on millions of lines of Java
code~\cite{fraser2014large}, both open-source code and close-source
code provided by one of our industrial partners.  In the previous two
editions of the unit testing tool competition, \EVOSUITE ranked
first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}.

@@

As the generated unit tests are meant for human
consumption~\cite{fraser2013does}, \EVOSUITE applies various
post-processing steps to improve readability (e.g., minimising) and
adds test assertions that capture the current behavior of the tested
classes. To select the most effective assertions, \EVOSUITE uses
mutation analysis~\cite{10.1109/TSE.2011.93}.  \EVOSUITE can also be
used to automatically find faults in the CUTs~\cite{emse13_oracle},
e.g., undeclared thrown exceptions and broken code contracts.  For
more details on the tool and its abilities we refer to~\cite{FrA11c},
and for more implementation details we refer to~\cite{FrA13a}.

%------------------------------------------------------------------------- 
\section{Competition Setup}

We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
for the search, with an earlier stop if the fitness value did not
increase for two minutes. The fitness function to drive the genetic
algorithm was based on a combination of line coverage, branch
coverage, and weak mutation testing. We enabled the post-processing
step of test minimization, but to reduce the time spent we included
all assertions rather than filtering them with mutation
analysis~\cite{10.1109/TSE.2011.93}. In practice, this may not result
in the most readable or maintainable test cases, but neither of these
two attributes is measured by the SBST contest metric.

@@

The results of \EVOSUITE on the benchmark classes are listed in
Table~\ref{table:results}. On average, \EVOSUITE achieved TODO line
coverage,TODO branch coverage\footnote{Using Cobertura's definition
  of branch coverage, which only counts conditional statements, not
  edges in the CFG.}, and TODO mutation score. On average, \EVOSUITE
produced TODO tests per class, and it took an average of TODO per class to
do so.
% (with \EVOSUITE configured to 3 minutes per class).

\subsection{Issues Encountered}

% CharMatcher: Timeout
% CycleHandler, WikipediaInfo: Infinite loop in generic resolving
% Response requires java.net.HttpURLConnection

Out of 63 CUTs, \EVOSUITE did not manage to obtain any coverage for 18
classes, i.e., 28\% of all classes.  For 14 of them (the 7 in the
twitter4j and the 7 in the hibernate projects), this is due to a
mismatch in libraries on the classpath.  In particular, \EVOSUITE does
bytecode instrumentation using the ASM library.  However, the projects
of the CUTs had their own (older) version of ASM.  This leads to
errors like: ``java.lang.IncompatibleClassChangeError: class
org.objectweb.asm.tree.ClassNode has interface
org.objectweb.asm.ClassVisitor as super class''.  Note: \EVOSUITE can
handle its own dependencies as CUTs, i.e., by using customized
classloaders, but only during the search phase.  In the generated
JUnit files, those have dependencies to ASM, as we do bytecode
instrumentation even there (e.g., to support environment testing based
on mock objects~\cite{arcuri2014automated}).  So, \EVOSUITE does
generate tests for those 14 classes, but then all those tests fails
due to that thrown exception.  An easy solution would be to ship
\EVOSUITE with its own ASM version using a different package name
(e.g., by using the JarJar
tool\footnote{https://code.google.com/p/jarjar/}).
%
If we had handled this issue properly before the competition, this
would have changed the result: Excluding classes from the twitter4j
and hibernate, the overall score of \EVOSUITE would be 191.584,
whereas GRT would have a score of 164.464. Consequently, this issue
clearly is the main factor affecting \EVOSUITE's overall result.

For the other four classes with 0\% coverage, \EVOSUITE failed to
generate any tests. For \<CharMatcher>, the issue is an issue in how
\EVOSUITE handled timeouts, which resulted in \EVOSUITE's master
process killing the client process before tests were written to
disk. For \<CycleHandler> and \<WikipediaInfo>, \EVOSUITE ran into an
issue when trying to resolve the generic type parameters of some
dependency classes. This issue could be avoided by omitting generic
type parameters, as the Java compiler would only issue warnings about
such missing parameters. However, as \EVOSUITE is aiming to produce
readable tests, we feel it is important to properly handle Java
Generics. Finally, for \<Response> the constructor requires a
parameter of type \<java.net.HttpURLConnection>, which is an abstract
class without concrete subclasses. As \EVOSUITE does not produce stubs
automatically, it therefore failed to instantiate \<Response> objects.

There are also a further 4 cases of low coverage (e.g., less than
30\%).  For example, if look at line coverage, then we have \<Page>
with 1.49\%, \<AbstractInstance> with 13.28\%,
\<CategoryDescendantsIterator> with 8.24\% and \<PageQueryIterable>
with 18.57\%.

TODO: Will look into these four.

%To improve \EVOSUITE, it will be important to
%understand why that was the case.

@@

With an overall score of $190.6$, \EVOSUITE achieved the second
highest score of all tools in the competition. The score calculated
for the best tool is $203.7$: a very close call.  In particular, if
considering only projects without a configuration issue in the
classpath of the target projects, \EVOSUITE would have scored first
with a score of $191.6$.
%
%due to
%a configuration issue in the classpath of the target projects,
%\EVOSUITE could had been run only on 7 out of 9 of the projects used
%as benchmark.  
The underlying issue can be easily fixed for future runs of the
competition.
% issue that would lead to even
%higher scores.
